Supplement - Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C

### 2024-09-16 submission/supplement.Rmd
supplementary fig 2

>>>>

\newpage
\begin{figure}
  \centering
  \includegraphics{../submission/compiled_figs/Supplement_WGBS.pdf}
  \caption[Loss of KDM5C impairs CpG methylation of germline gene promoters]{\textbf{[Loss of KDM5C impairs CpG methylation of germline gene promoters.} \textbf{A.} Volcano plot of whole genome bisulfite sequencing (WGBS) for all gene promoters in wild-type (WT) versus \textit{Kdm5c}-KO extended EpiLCs (exEpiLCs). Significantly differentially methylated promoters (q < 0.01, |methylation difference| > 25\%). Germline promoters highlighted in green, non-germline promoters in light blue, non-significant promoters in gray. \textbf{B.} enrichPlot gene ontology of all promoters significantly hypomethylated in \textit{Kdm5c}-KO exEpiLCs.}
  \label{figurelabel}
\end{figure}
